Classless Java

### 2015-09-20 paper/sections/Overview.tex
revise overview for the shorter Point example.

We provide a Java annotation \mixin to provide default implementations for
various methods and a mechanism to instantiate objects. \mixin annotation helps
programmers to write less cumbersome code and instantiate interfaces in Java.

@@

\texttt{Point} has two (conceptually) member fields \texttt{X} and
\texttt{Y}. Methods \texttt{int X()} and \texttt{int Y()} serve as \emph{getter}
methods. Methods \texttt{void X(int X)} and \texttt{void Y(int Y)} serve as
\emph{setter} methods. Method \texttt{Point withX(int X)} updates field
\texttt{X} and returns \textbf{this}.

@@

\lstinputlisting[linerange=82-112]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINTIMPL

@@

Inside the anonymous class in the annotated interface, the following code are
generated:
\begin{itemize}
\item For methods inside the interface with the form \texttt{Tx x()}:
  \begin{itemize}
   \item \texttt{x} is the getter method, with return type
     \texttt{Tx}. Conceptually, it is a member field with name \texttt{x} and
     type \texttt{Tx}.
   \item generate member field \texttt{\_x} of type \texttt{Tx}, initialized
     with \texttt{x}.
   \item generate implemented getter method:
       \begin{lstlisting}
           public Tx x() { return _x; }
       \end{lstlisting}
   \end{itemize}

>>>>

We provide a Java annotation \mixin to provide default implementations for
various methods and a mechanism to instantiate objects. \mixin annotation helps
programmers to write less cumbersome code and instantiate interfaces in
Java. More over, with \mixin annotation, programmers can mimic multiple
inheritance in a restricted form easily.

@@

\texttt{Point} has two (conceptually) member fields \texttt{X} and
\texttt{Y}. Methods \texttt{int X()} and \texttt{int Y()} serve as \emph{getter}
methods. % Methods \texttt{void X(int X)} and \texttt{void Y(int Y)} serve as
% \emph{setter} methods. Method \texttt{Point withX(int X)} updates field
% \texttt{X} and returns \textbf{this}.

@@

\lstinputlisting[linerange=33-46]{../UseMixinLombok/src/overview/TestPoint.java} % APPLY:linerange=POINTIMPL

@@

Apart from generating code for \emph{getter} methods, the annotation processor
can also generate \emph{setter} methods, \emph{with} methods, \texttt{clone}
methods, etc. We summarize all the forms of method \mixin  supports below. Inside
the anonymous class in the annotated interface, the following code are
generated:

\begin{itemize}
\item For methods inside the interface with the form \texttt{Tx x()}:
  \begin{itemize}
   \item \texttt{x} is the getter method, with return type
     \texttt{Tx}. Conceptually, it is a member field with name \texttt{x} and
     type \texttt{Tx}.
   \item generate member field \texttt{\_x} of type \texttt{Tx}, initialized
     with \texttt{x}.
   \item generate implemented getter method:
       \begin{lstlisting}
           public Tx x() { return _x; }
       \end{lstlisting}
   \end{itemize}
